A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-08 main.tex
Revise abstract.

@@

    We develop yet another typed multi-stage calculus \LMD.
    It extends Hanada and Igarashi's \LTP with dependent types.
    A multi-stage calculus enables us to generate and execute codes at runtime.
    It can improve the performance of programs by generating optimized codes for given inputs.
    Dependent types are types dependent on values. 
    A vector with its length is a famous example of dependent types and it enables us to omit boundary checking.
    In this paper, we design \LMD by introducing dependent type into $\lambda^{\TW\%}$.
    You can make more efficient programs from existing dependent typed programs with \LMD.
    \LMD has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
    It also includes an evaluation context which satisfies unique decomposition.
    The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
    Especially, the way of handling CSP in equivalence rules of dependent types wasn't clear.
    In this paper, we give reasonable equivalence rules to handle them.

>>>>

\newcommand{\AI}[1]{\textcolor{red}{[#1 -- AI]}}

@@

  We study a dependently typed extension of a multi-stage programming
  language \`a la MetaOCaml, which supports quasi-quotation and
  cross-stage persistence for manipulation of code fragments as
  first-class values and run for execution of programs dynamically
  generated by the code manipulation.  Dependent types are expected to
  bring to multi-stage programming enforcement of strong
  invariants---beyond simple type safety---on the behavior of
  dynamically generated code.  An extension is not trivial, however,
  because a type system would have to take stages---roughly speaking,
  the number of surrounding quotations---of types into account.

  To rigorously study properties of such an extension, we develop
  \LMD, which is an extension of Hanada and Igarashi's typed calculus
  \LTP with dependent types, and prove its properties including
  subject reduction, confluence, strong normalization for full
  reduction, and progress \AI{?} for evaluation semantics.  Motivated
  by code generators such that the type of generated code depends on a
  value from an earlier stage, we argue the significance of
  cross-stage persistence in dependently typed multi-stage programming
  and certain type equivalence that are not directly derived from
  reduction rules.

    % A multi-stage calculus enables us to generate and execute codes at runtime.
    % It can improve the performance of programs by generating optimized codes for given inputs.
    % Dependent types are types dependent on values. 
    % A vector with its length is a famous example of dependent types and it enables us to omit boundary checking.
    % In this paper, we design \LMD by introducing dependent type into $\lambda^{\TW\%}$.
    % You can make more efficient programs from existing dependent typed programs with \LMD.
    % \LMD has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization, and progress.
    % It also includes an evaluation context which satisfies unique decomposition.
    % The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
    % Especially, the way of handling CSP in equivalence rules of dependent types wasn't clear.
    % In this paper, we give reasonable equivalence rules to handle them.
